---
title: 'Supplemental Material: Reciprocity supports cooperation in real-world collective action networks'
header-includes:
      - \usepackage{dcolumn}
output:
  pdf_document:
    fig_caption: yes
    extra_dependencies: ["float"]
bibliography: refs.bib     
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE)
knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
library(tidyverse)
library(stringr)
library(knitr)
library(kableExtra)
library(cowplot)
#reset working directory
getwd()->wd
new_wd <- str_remove(wd,"/supplemental materials")
setwd(new_wd)
source("Code/k_means.R")
load("Data/Reciprocity.Rdata")
load("Data/Sensitivity_model.Rdata")
load("Data/FC_sensitivity_values.Rdata")
rename(all.clubs, Club = `Club Number`)->all.clubs

```

### Sample Characteristics

The clubs in our data set are samples from WEIRD [@apic2020;@hen2020;@hen2010] countries: 2 from Australia, 1 from Canada and the rest from the United States. One software provider gave us access to their whole catalog of groups, which included the 3 from outside of the United States, and the other only gave us access to their clubs located in New England. The sample includes defunct and still functioning clubs (as of the end of the data period), where the average lifespan of defunct clubs was 3.16 years (2.16 SD) and 28.7 orders (21.3 SD), while the censored average lifespan for continuing clubs is 3.24 years (1.38SD) and 46.9 orders (27.9 SD). The average number of members participating in an order is 7.96 for defunct clubs (6.96 SD) and 12.7 for ongoing (9.41 SD). Additionally, the average number of co-purchased items in each order is 3.29 for defunct clubs (4.82 SD) and 11.2 for ongoing clubs (28.9 SD). 


```{r summary stats,warning=FALSE,message=FALSE}
options(knitr.kable.NA = '')
mutate(all.clubs, Orders = map(graphs, ~length(.x)))%>%
  mutate(Members = map(member.types, ~filter(.x, !is.na(type))%>%nrow()))%>%
  select(Club,Orders,Members,stab)%>%
  unnest()%>%
  ungroup()%>%
  mutate_at(.vars = 8:11,.funs = function(x){x*100})%>%
  mutate_at(.vars = 4:11,.funs = round,digits = 2)%>%
  mutate(Club = as_factor(Club))%>%
  select(Club,Orders, Members, pwd,pbd,pwi,pbi,CV.pwd,CV.pbd,CV.pwi,CV.pbi)->t
  colnames(t)[4:11]<-rep(c("DWR","DBR","IWR","IBR"),2)
  colSums(t[,2:3],na.rm = TRUE)->sums
  round(colMeans(t[4:11],na.rm = TRUE),2)->means
  rbind(t,c(36,sums,means))->t
  kbl(t,booktabs = TRUE,caption = "Share-based Reciprocal Edge Classifications and Coefficients of Variation")%>%
    kable_styling(latex_options = c("striped"))%>%
    add_header_above(c(" "=3,"Percent of Total Edges"=4,"Coefficient of Variation"=4))%>%
    pack_rows("Totals",36,36)
    
  
```

```{r robustness summary,warning=FALSE,message=FALSE}
options(knitr.kable.NA = '')
filter(sense,analysis == "sens")%>%
  select(`Club Number`,recip,value)%>%
  mutate(value = round(value*100,1))%>%
  spread(recip,value)%>%
  select(`Club Number`,pwd,pbd,pwi,pbi)->t
  colnames(t)[2:5]<-c("DWR","DBR","IWR","IBR")
  round(colMeans(t[2:5],na.rm = TRUE),1)->means
  rbind(t,c(NA,means))->t
  kbl(t,booktabs = TRUE,caption = "Purchase Order-based Reciprocal Edge Classifications")%>%
    kable_styling(latex_options = c("striped"))%>%
    add_header_above(c(" "=1,"Percent of Total Edges"=4))%>%
    pack_rows("Means",14,14)
  
```


```{r Mixed effects 1, echo = FALSE, results='asis'} 
#All Edges
select(all.clubs,Club,degree.balance)%>%#select degree balance data
  unnest()%>%#unnest
  group_by(Club,Purchaser)%>%#group by club name and purchaser
  summarize_at(.vars = c("In.Degree","Out.Degree"),.funs = sum)->RE#aggregate each purchaser's in and out degree

rename(RE,`Out Degree` = Out.Degree,
       `In Degree` = In.Degree)->RE

lme4::lmer(`Out Degree`~`In Degree` + (1|Club) ,data=RE)->re.model
#Single Assistance Edges
select(all.clubs,Club,single.assistance)%>%#select singular assistance data
  unnest()->RE.SA#unnest data
rename(RE.SA,`Out Degree` = Given,
       `In Degree` = Received)->RE.SA
RE.SA.model <- lme4::lmer(`Out Degree`~`In Degree`+(1|Club),data = RE.SA)#estimate mixed effects model
#Sensitivity Analysis
select(sense_edges,parent_id,edges)%>%
  unnest()%>%
  unnest()->model_edges
  
model_edges%>%group_by(parent_id,from)%>%
  count(name = "Out Degree")->out
model_edges%>%group_by(parent_id,to)%>%
  count(name = "In Degree")->in.d  
  
inner_join(out,in.d,by=c("from"="to","parent_id"))%>%
  rename(Club = parent_id)->rob_edges

lme4::lmer(`Out Degree` ~ `In Degree` + (1|Club),data = rob_edges)->rob_model

broom.mixed::tidy(re.model)%>%filter(effect == "fixed")->ae
broom.mixed::tidy(RE.SA.model)%>%filter(effect == "fixed")->sae
broom.mixed::tidy(rob_model)%>%filter(effect == "fixed")->rae
sd_re<-round(as.numeric(attributes(lme4::VarCorr(re.model)$Club)$stddev), 2)
sd_sa_re<-round(as.numeric(attributes(lme4::VarCorr(RE.SA.model)$Club)$stddev), 2)
sd_ro_re<-round(as.numeric(attributes(lme4::VarCorr(rob_model)$Club)$stddev), 2)
REML<-round(re.model@devcomp$cmp[7],2)
REML_sa <- round(RE.SA.model@devcomp$cmp[7],2)
REML_rob<- round(rob_model@devcomp$cmp[7],2)
mod.stats <- tribble(~stat, ~re.model, ~RE.SA.model,~rob_model,
                     "Random Effects:",NA,NA,NA,
                     "Standard Deviation",sd_re,sd_sa_re,sd_ro_re,
                     "Clubs",35L,35L,13L,
                     "Observations", nrow(RE),1113,263,
                     "REML",REML,REML_sa,REML_rob,
                     "AIC",round(AIC(re.model),2),round(AIC(RE.SA.model),2),round(AIC(rob_model),2))

stargazer::stargazer(re.model,RE.SA.model,rob_model,
                     coef = list(ae$estimate,sae$estimate,rae$estimate),
                     se = list(ae$std.error,sae$std.error,rae$std.error),
                     no.space = TRUE,
                     header=FALSE,
                     align = TRUE,
                     single.row = FALSE,
                     font.size = "small",
                     intercept.bottom = F,
                     column.labels = c("All Edges","Singular Assistance\nEdges","Robustness Check"),
                     omit.table.layout = "s",
                     dep.var.labels = "Out Degree",
                     covariate.labels = c("Global Mean Intercept","In Degree"),
                     # ...but supply your own that you created (with random effects)
                     add.lines = lapply(1:nrow(mod.stats), function(i) unlist(mod.stats[i, ])),
                     title = "Mixed Effects Models")

```


```{r cluster centers,echo = FALSE,warning=FALSE,fig.align='center'}
mutate(all.clubs, centers = map(degree.balance, ~pluck(k_means(.x$SPR),"centers")))%>%
  select(Club,centers)%>%
  unnest()%>%
  spread(type,center)%>%
  select(Club,Beneficiary,Reciprocator,Helper)%>%
  mutate(Beneficiary = round(Beneficiary,3),
         Helper = round(Helper,3))%>%
  kableExtra::kbl(caption = "SPR Cluster Centers",align = c("l","c","c","c"),booktabs = TRUE)

```


```{r member types,echo = FALSE,warning=FALSE,fig.align='center'}
select(all.clubs,Club, member.types)%>%
  unnest()%>%
  group_by(Club)%>%
  count(type)%>%
  spread(type,n,fill=0)%>%
  rename(Beneficiaries = B,
         Helpers = H,
         Reciprocators = R, 
         `Unclassified*` =`<NA>`)%>%
  select(Club,Beneficiaries,Reciprocators,Helpers,`Unclassified*`)->t
  bind_rows(t,tibble(Club = NA,Beneficiaries=sum(t$Beneficiaries),Reciprocators=sum(t$Reciprocators),Helpers=sum(t$Helpers),`Unclassified*`=sum(t$`Unclassified*`)))->t
  kableExtra::kbl(t,caption = "Count of Member Types",booktabs = T,align = c("l",rep("c",4)))%>%
  footnote(general = "* Members who only participate in one order do not have a Markov matrix and thus remain unclassified",
           threeparttable = TRUE)%>%
    pack_rows("Totals",36,36)
```

### References